---
title: |
  | INFS_SP5_2023
  | DATA VISUALISATION
  | Assessable Exercise 2
author: "Enna H"
output: 
  pdf_document:
    toc: true
editor_options:
  chunk_output_type: console
---


```{r echo = FALSE, include=FALSE}
# clear all variables, functions, etc
# clean up memory
rm(list=ls())
# clean up memory
gc()
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, 
  fig.width = 8, 
  fig.asp = 0.618, 
  out.width = "80%",
  fig.align = "center", 
  root.dir = "../",
  message = FALSE,
  size = "small"
)
```



```{r warning=FALSE, include=FALSE}
pacman::p_load(tidyverse)
pacman::p_load(knitr,dplyr,AICcmodavg)
pacman::p_load(inspectdf,tidyr,stringr, stringi,DT,mice)
pacman::p_load(caret,modelr)
pacman::p_load(mlbench,mplot)
pacman::p_load(tidymodels,glmx)
pacman::p_load(skimr,vip,yardstick,ranger,kknn,funModeling,Hmisc)
pacman::p_load(ggplot2,ggpubr,GGally)
knitr::opts_chunk$set(message = FALSE)
```


```{r warning=FALSE, include=FALSE}
# Decision tree
pacman::p_load(rpart.plot)

# Data manipulation
pacman::p_load(rgl, rattle, mice, dplyr, tidyverse)

# Plotting
pacman::p_load(viridis, hrbrthemes, ggplot2, heplots, forcats)
pacman::p_load(beeswarm, quantmod, reshape2, plyr, scales, streamgraph, viridis, zoo)
```

```{r}
# read the data
# customer count
ccount <- read.csv("ccount.csv",header=T)
head(ccount)
ccount <- na.omit(ccount)
```

```{r}
# demographics
demo <- read.csv("demo.csv",header=T)
head(demo)
demo <- na.omit(demo)
```
This next set of data files are the result of aggregating the data to massage the original
data into providing more information.  This might provide inspiration.


Beer_agg.csv is the result of aggregating across the beer data.

```{r}

beern <- read.csv("Beer_agg.csv",header=T,strip.white=TRUE)
head(beern)
beern <- na.omit(beern)

```

```{r}
# STORE_ZONE_SUM_PT.csv is the result of aggregating across the data to capture
# store information across zones and price tiers.  This data needed some extra cleaning, 
# hence the extra lines of code below
SZSP <- read.csv("STORE_ZONE_SUM_PT.csv",header=T,strip.white=TRUE)
head(SZSP)
SZSP <- SZSP[,-1]
SZSP <- na.omit(SZSP)
SZSP$ZONE <- factor(SZSP$ZONE)
```

```{r}
# check the data - there's a weird entry that is blank
table(SZSP$Price_Tier)

```

```{r}
# Clean the blank entry
SZSP <- SZSP[SZSP$Price_Tier != "",]
SZSP$Price_Tier <- factor(SZSP$Price_Tier)

```

```{r}
# check the data again - it should be fine now :)
table(SZSP$Price_Tier)   # and it is!

```

```{r}
# Now do the same for this summary of beer data
df <- read.csv("Beer_MPPPTB.csv",header=T,strip.white=TRUE)
df <- df[,-1]
table(df$Price_Tier)
df <- df[df$Price_Tier != "",]
df$Price_Tier <- factor(df$Price_Tier)
table(df$Price_Tier)


```

```{r}
# And do the same one more time for this file :)
# CHE_Summary.csv is the result of aggregating across the cheese data
ch <- read.csv("CHE_Summary.csv",header=T,strip.white=TRUE,stringsAsFactors=F)
head(ch)
ch <- ch[,c(-1,-2,-22)]
ch <- na.omit(ch)
table(ch$Price_Tier)
ch <- ch[ch$Price_Tier != "",]
ch$Price_Tier <- factor(ch$Price_Tier)
table(ch$Price_Tier)

```

```{r}
# We also did some specific beer brand analysis
bm <- read.csv("Bud-vs-Miller-dates-GOOD.csv",header=TRUE)
head(bm)

```

# Dotplots

- Dotplot of cheese data - isolate a week of interest
```{r}
idx <- which(ch$"WEEK"==9)
length(idx) 
dplot_df <- ch[idx,c(1,8)]

```
- cheese stores
```{r}
STORES <- c(5,9,12,14,32,40,49,52,56,62,70,71,78,80,81,84,86,93,97,100,102,104,113,115,116, 118, 119, 124, 126, 130)
dx <- match(STORES,dplot_df$STORE)

idx <- which(dplot_df$Profit_Count!=0)
dplot_df <- dplot_df[idx,]

```
- isolate a store of interest
```{r}
dplot_df$fact <- ifelse(dplot_df$STORE==94,'Y','N')
head(dplot_df)

```
- Plot Total Profit/Store in Week 9 and highlight store 94
- you will need to re-size the graph to see the labels 
```{r}
ggplot(dplot_df,aes(x=factor(STORE),fill=factor(fact),y=Profit_Count)) + 
       geom_dotplot(binaxis = "y", stackdir = "center") + 
       xlab("Store") + ylab("Total Profit ($USD)") + 
       theme(legend.position="none",axis.title=element_text(size=14), axis.text=element_text(size=12)) + 
       scale_fill_manual(values=c("#8595E1","#E07B91")) + 
       theme(text = element_text(size=20),axis.text.x = element_text(angle=90, hjust=1)) 


```
# Boxplots (Original, Notched, Violin) 


-  Boxplot of Sum 
```{r}
ggplot(SZSP, aes(x=ZONE, y=Sum, fill=ZONE)) + 
       geom_boxplot() +
       theme(legend.position="none") +
       ylab("Sales Volume")

```

- Boxplot Notched (False/True)

```{r}
ggplot(SZSP, aes(x=ZONE, y=Sum, fill=ZONE)) + 
       geom_boxplot(outlier.colour="black", outlier.shape=16,outlier.size=2, notch=FALSE) + 
       theme(axis.title=element_text(size=14),axis.text=element_text(size=12),legend.position="none") + 
       ylab("Beer Sales (Volume)\n") + xlab("\nZone")

```


## Violin Plot


```{r}
ggplot(SZSP, aes(x=ZONE, y=Sum, fill=ZONE)) + 
       geom_violin() + 
       theme(text = element_text(size=14),legend.position="none") + 
       ylab("Beer Sales (Volume)\n") + xlab("\nZone")


```
## Boxplots by group
```{r}
ggplot(aes(y = Sum, x = BRAND, fill = Price_Tier), data = bm) + 
      geom_boxplot() + 
      theme(panel.background = element_rect(fill ="white"), panel.grid.major = element_line(colour = "#BFC1C9"), 
        axis.title=element_text(size=14),axis.text=element_text(size=12)) +
      ylab("Number of units sold per week\n") + xlab("\nBrand") + 
      scale_fill_manual(values=c("#ffffff","#cce8f8", "#000000","#E69F00"))


```
## Boxplot Sales by Zone, filled by Price Tier
```{r}
ggplot(SZSP, aes(ZONE, Sum, fill = factor(Price_Tier))) + 
        scale_y_continuous(breaks=seq(0,3500,by=500)) + 
        theme(axis.text.x = element_text(size=14,hjust = 1,vjust = 1)) + 
        xlab("Zone") + ylab("Beer Sales (Volume)") + 
        guides(fill=FALSE) + 
        geom_boxplot() + facet_grid(.~Price_Tier, scales="free")


```
## Boxplot Sales by Store, filled by Price Tier
```{r}
ggplot(beern, aes(factor(STORE), Sum, fill = factor(Price_Tier))) +
     scale_y_continuous(breaks=seq(0,3500,by=500)) +
     theme(axis.text.x = element_text(size  = 6,angle = 90,hjust = 1,vjust = 1)) +
     xlab("Store") + ylab("Beer Sales (Volume)") +
     guides(fill=FALSE) +
     geom_boxplot() +
     facet_grid(.~Price_Tier, scales="free")

```


# Rainfall Plot 

```{r}
ggplot(beern, aes(factor(STORE), Sum)) + 
        theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
        xlab("Store") + ylab("Beer Sales (Volume)\n")  + 
        geom_point(color='#149EF3') + 
        theme(text = element_text(size=14),legend.position="none")
```


```{r}

ggplot(SZSP, aes(ZONE, Sum)) +
     theme(axis.text.x = element_text(hjust = 1)) +
     xlab("Zone") + ylab("Beer Sales (Volume)\n")  +
     geom_point(color='#DD3497') +
     theme(text = element_text(size=14),legend.position="none")


```
# Bubble & Swarm Plots 


## Bubble Plots
```{r}
df1 <- df
df2 <- as.data.frame(sapply(df,gsub,pattern="High",replacement="H"))
df2 <- as.data.frame(sapply(df2,gsub,pattern="Low",replacement="L"))
df2 <- as.data.frame(sapply(df2,gsub,pattern="Medium",replacement="M"))
df2 <- as.data.frame(sapply(df2,gsub,pattern="CubFighter",replacement="C"))

df1$Price_Tier <- df2$Price_Tier
```


## Profit by zone 
```{r}
radius <- sqrt(df1$MOVE/ pi )
          symbols(df1$PRICE, df1$PROFIT, circles=radius, inches=0.35, fg="white", bg="#E7298A", xlab="Price", ylab="Profit")
          text(df1$PRICE, df1$PROFIT, df1$Price_Tier, cex=0.5)

```

```{r}
cbbPalette <- c("#000000", "#56B4E9", "#D55E00",  "#CC79A7")
pt <- as.factor(df$Price_Tier)
ggplot(df,aes(x=df$PRICE, y=df$PROFIT, group=pt,shape=pt,size=radius,colour=df$Price_Tier)) +
              scale_shape_manual(values=c(15,16,17,18)) + 
              scale_colour_manual(values=cbbPalette) + 
              theme(panel.background = element_rect(fill ="white"), panel.grid.major = element_line(colour = "#BFC1C9")) + 
              geom_point( alpha=0.8) +  
              guides(colour = FALSE, shape = guide_legend(order = 1)) + 
              labs(shape = "Price Tier",size="Scale") +
                scale_x_continuous("Beer Price (volume)") + 
                scale_y_continuous("Beer Profit (volume)")

```

```{r}
ggplot(df, aes(df$PRICE, y=df$PROFIT, colour=df$Price_Tier, size=radius)) + 
    geom_point( alpha=0.8) + 
    scale_colour_brewer(palette="Spectral", type="qual",name="Price Tier") +
    guides(colour = guide_legend(override.aes = list(alpha = 1))) +
    scale_x_continuous("Cheese Price") + 
    scale_y_continuous("Cheese Profit (gross margin)")

```
## Swarm Plots

print(unique(df1$Price_Tier))

```{r}
# Load Required Libraries
pacman::p_load(ggbeeswarm)
```

```{r}

# ggplot2 Swarm Plot
ggplot(SZSP, aes(x = Price_Tier, y = Sum, color = Price_Tier)) +
  geom_beeswarm() +
  scale_color_manual(values = c("#32AAB5", "#60C4BC", "#8CD9C0", "#B3E7C5")) +
  labs(x = "Price Tier", y = "Profit") +
  theme_minimal()

```

```{r}
head(SZSP)
head(df1)
```

```{r}
# ggplot2 Swarm Plot
ggplot(df1, aes(x = Price_Tier, y = PRICE, color = Price_Tier)) +
  geom_beeswarm() +
  scale_color_manual(values = c("#32AAB5", "#60C4BC", "#8CD9C0", "#B3E7C5")) +
  labs(x = "Price Tier", y = "Profit") +
  theme_minimal()

```



# 100% Stacked Bar 

## cheese data 
## Count by Price Tier
```{r}
p <- ggplot(aes(x=WEEK, weight=Count, fill=Price_Tier), data=ch)
p + geom_bar(position='fill') + scale_y_continuous(labels = percent) +   
    scale_fill_brewer(palette="PuOr") + 
    labs(x="X Label", y="Y Label", title="An Example Stacked Column Percentage Chart")

```
# Average Price by Price Tier
```{r}
p <- ggplot(aes(x=WEEK, weight=Price_Mean, fill=Price_Tier), data=ch)
p + geom_bar(position='fill') + scale_y_continuous(labels = percent_format()) +   
     scale_fill_brewer(palette="Spectral") + theme(axis.title=element_text(size=14),axis.text=element_text(size=10)) +
     labs(x="Weeks of the Year", y="Average Beer Price ($USD)")

```



# Calendar Heat Map 

```{r}
head(ch)
```

```{r}
# Load Required Libraries
pacman::p_load(lubridate)
```

```{r}
# Save Original Data
safe <- ch
pal <- colorRampPalette(c("#010184", "#b0f0b0"))

# Remove invalid Dates
ch <- ch %>% filter(!is.na(dmy(Date)))
```
```{r}
# Apply transformations
ch <- ch %>%
  mutate(
    Date = dmy(Date),
    year = year(Date),
    month = month(Date),
    monthf = factor(month, levels = 1:12, labels = month.abb, ordered = TRUE),
    weekday = wday(Date),
    weekdayf = factor(weekday, levels = 1:7, labels = c('Mon', 'Tue', 'Wed', 'Thu', 'Fri', 'Sat', 'Sun'), ordered = TRUE)
  ) %>%
  group_by(year, month) %>%
  mutate(
    week = week(Date),
    monthweek = 1 + week - min(week)
  )

```

```{r fig.height=12, fig.width=16}

# Calculate the week of the month
ch <- ch %>% mutate(day = day(Date), monthweek = ceiling(day / 7))

# Remove NAs
ch <- ch %>% filter(!is.na(monthweek) & !is.na(weekdayf) & !is.na(Profit_Mean))



# Plot
ggplot(ch, aes(x = monthweek, y = weekdayf, fill = Profit_Mean)) +
  geom_tile(color = "white") +
  facet_grid(year ~ monthf) +
  scale_fill_gradientn(colors = pal(10)) +
  theme(
    panel.background = element_rect(fill = "white"),
    panel.grid.major = element_line(color = "#BFC1C9"),
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 10)
  ) +
  xlab("Week of Month") +
  ylab("")

```
```{r}
# Restore Original Data
ch <- safe
```

